Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-09-25 reviews/reviewer3-response.md

>1. For convergence study, Fig 5 gives the results for different choice of time step. however, for SST model, the Cp do not convergent with the time step. On the other hand, the choice of time step is always coupled with the choice of space step. Generally speaking, the time step cannot be too small for a certain space discretion condition. Therefore, It is suggested that the author provide this relationship between space and time discretion.

It is true that in general spatial and temporal discretization are coupled.
However, using the PIMPLE solver in OpenFOAM allows for stable solutions even
when the CFL condition is not satisfied in every cell. In our case, we used a
fixed time step, such that it would not be changed by the solver based on the
Courant number. For example, the temporal convergence data shown were acquired
using the "final" spatial resolution and vice versa. This did take some
iterative process, but ultimately we have one independent variable for each
plot. A note has been added to the manuscript to clarify this point.

>2. No the convergence study for 3d model in this paper.

This is true, we did not perform a true convergence study for the 3-D model. We
simply extrapolated the 2-D grid into three dimensions. While this may not be
ideal, this strategy may be useful to practitioners looking to perform similar
simulations, but do not have the computational resources to perform multiple
high fidelity 3-D simulations. The paper has been adjusted to clarify this
point.

### 2016-09-25 paper.tex
Note that a 3-D grid convergence study was not done

>>>>

Sensitivity to spatial resolution and time step was not assessed for the 3-D
case, as the computational cost would have been prohibitive. However, the mesh
resolution in the $x$--$y$ plane and time step were chosen based on the 2-D
results. Selecting a grid and time step in this way presents an alternative that
may be useful to practitioners who do not have access to the computationl
resources necessary to perform multiple high fidelity 3-D simulations.
